---
title: "131 HOMEWORK 2"
author: "Katherine Bayt"
date: '2022-04-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrplot)
library(ggthemes)
tidymodels_prefer()
library(ISLR)
library(yardstick)
abalone <- read.csv("C:\\abalone.csv")
```

## QUESTION 1

```{r echo = FALSE}
abalone <- abalone %>%
  mutate(age = abalone$rings + 1.50)
abalone %>% ggplot(aes(x=age))+ geom_histogram(bins=60)

```

The distribution of age is numeric with a range from 2 to 32. Age has the highest counts at 12, with higher counts to the left of 12, and lower counts to the right os 12. The distribution is right skewed, with a larger range of ages to the right of the highest count age.

## QUESTION 2

```{r}
set.seed(4857)
abalone$rings = NULL
abalone_split <- initial_split(abalone, prop = 0.8,
                                strata = age)
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)
```

## QUESTION 3

```{r}
abalone_recipe <- recipe(age ~ ., 
                         data = abalone_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms=~starts_with("type"):shucked_weight) %>%
  step_interact(terms=~longest_shell:diameter) %>%
  step_interact(terms=~shucked_weight:shell_weight) %>%
  step_normalize(all_predictors())
summary(abalone_recipe)
view(abalone_train)
```

We should not use rings to predict age because they have a positive correlation of 1. Thus, when predicing age, the model will predict age as the value of rings. \## QUESTION 4

```{r}
lm_model <- linear_reg() %>%
  set_engine("lm")
```

## QUESTION 5

```{r}
lm_wflow <- workflow() %>%
  add_model(lm_model) %>%
  add_recipe(abalone_recipe)
```

## QUESTION 6

```{r}
lm_fit <- fit(lm_wflow, abalone_train)
lm_fit
df <- data.frame(longest_shell = 0.5, diameter = 0.10,
                 height = 0.30, whole_weight = 4,
                 shucked_weight = 1, viscera_weight = 2,
                 shell_weight = 1, type = "F")
predict(lm_fit, new_data = df)
```

## QUESTION 7

```{r}
abalone_train_res <- predict(lm_fit, new_data = abalone_train %>%
                               select(-age))
abalone_train_res <- bind_cols(abalone_train_res,
                               abalone_train %>% select(age))
abalone_train_res %>% head()

abalone_metrics <- metric_set(rmse, rsq, mae)
abalone_metrics(abalone_train_res, truth = age, estimate = .pred)

```

Overall, we get a r-squared value of 0.55, showing that about 55% of our training data fits the regression model. Thus, the regression model does not do a very good job of predicting age within the training set.
